Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375

### 2015-01-15 papers/B1555_EdgeOn/B1555_letter.tex
add best-fit parameters of 2-SIE model

\section{Lens Modeling}
To model B1555+375, we use the lens modeling code $glafic$ \citep{Oguri} with known position and flux data from the radio observation done by \citet{Marlow}. Morlow et al. first published the flux ratio anomaly detection and lens model of B1555+375. However, their SIE lens model cannot explain the flux ratio anomaly between image A and B (see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band image (Fig. 1, left), a recognizable edge-on disk is lie in the center with position angle $~10$ degree. With this information, we model B1555+375 with SIE for bulge and exponential disk model for edge-on disk. The full best-fit parameters are shown in Table 1. We also try on another model with two SIE mass profiles. This model will be used in the following up study with Simona...

The comparison of radio observation and our modeling result is in Figure 2, Table 2 \& 3.\\

@@

\begin{figure}
\plotone{point_source.eps}
\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$, marked by a black filled circle. From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
\end{figure}

%%table1
\begin{table}
\begin{center}
\caption{Lens Model Best-Fit Parameters.\label{tbl-1}}
\begin{tabular}{lcccccc}
%%\tableline\tableline
Model &		&		 &  \\
\tableline\tableline
SIE 	& $x$		& $y$ 		& $\sigma (km/s)$ 	& $e$	& $\theta$  \\  
		&$-0.1883$ 	&$-0.1923$	&$93.74$ 			&$0.27$	& $105.5 \degr$   \\
\tableline
Expdisk	& $x$		& $y$		& $M_{tot} (h^{-1}M_{\odot})$	& $e$	& $\theta$	& $r_e$ \\
		&$-0.1615$  &$-0.2502$	&$1.19\times 10^{10} $ 			&$0.84$ &$7.4 \degr$& $0.20 ''$  \\

\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Positions are offsets from component A measured in unit of arcsec. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
\end{center}
\end{table}

>>>>

\section{Lens Modeling}
To model B1555+375, we use the lens modeling code $glafic$ \citep{Oguri} with known position and flux data from the radio observation done by \citet{Marlow}. Morlow et al. first published the flux ratio anomaly detection and lens model of B1555+375. However, their SIE lens model cannot explain the flux ratio anomaly between image A and B (see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band image (Fig. 1, left), a recognizable edge-on disk is lie in the center with position angle $~10$ degree. With this information, we model B1555+375 with two models. The first model consists of an SIE bulge and an exponential edge-on disk(SIE+Expdisk). The second model consists of two SIE mass profiles, for bulge and disk respectively. The full best-fit parameters are shown in Table 1. Both of these models predict fairly matched results with the radio observation. The comparison of observation and SIE+Expdisk result is in Figure 2, Table 2 \& 3.\\

@@

\begin{figure}
\plotone{point_source.eps}
\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle. From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
\end{figure}

%%table1
\begin{table}
\begin{center}
\caption{Lens Model Best-Fit Parameters.\label{tbl-1}}
\begin{tabular}{lcccccc}
%%\tableline\tableline
SIE&		&		 &  \\
+Expdisk\\
\tableline\tableline
SIE& $x$		& $y$ 		& $\sigma $ 	& $e$	& $\theta$  \\
	&					&					&  (km/s)			&			&						\\
		&$-0.1883$ 	&$-0.1923$	&$93.74$ 			&$0.27$	& $105.5 \degr$   \\
\tableline
Expdisk	& $x$		& $y$		& $M_{tot} $					& $e$	& $\theta$	& $r_e$ \\
				&				&				& $(h^{-1}M_{\odot})$	&			&						&				\\
		&$-0.1615$  &$-0.2502$	&$1.19\times 10^{10} $ 			&$0.84$ &$7.40 \degr$& $0.20 ''$  \\  
\tableline\tableline
2-SIE\\
\tableline
Bulge& $x$				& $y$ 		& $\sigma $ 	& $e$	& $\theta$  \\  
			&					&					&  (km/s)			&			&						\\
						&$-0.1809$ 	&$-0.1702$& $81.67$ 					&$0.27$	& $97.71 \degr$   \\
\tableline
Disk\\
						&$-0.1592$ 	&$-0.1833$& $69.91$ 					&$0.83$	& $7.40 \degr$   \\
\tableline

\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Positions are offsets from component A measured in unit of arcsec. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
\end{center}
\end{table}
